\section{Thesis Organisation}

This thesis is organised into the chapters as outlined below. An appendix follows with additional supplementary material.

\paragraph{Chapter \ref{ch:background_work} - Background Work} Provides an overview of prior studies broadly around the areas of number recognition in image processing and artificial neural networks.

\paragraph{Chapter \ref{ch:related_work} - Related Work} Documents a number case studies within the literature directly or closely related to the aims of this research.

\paragraph{Chapter \ref{ch:research_methodology} - Research Methodology} Describes possible techniques in closer depth to develop a number recognition pipeline, and explores ways to develop prominence ranking techniques.

\paragraph{Chapter \ref{ch:benchmarking} - Benchmarking} Collates results of a series of experiments using our dataset amongst other tools and pipelines currently developed.

\paragraph{Chapter \ref{ch:processing_pipeline} - Processing Pipeline} Discusses the proposed processing pipeline developed that satisfies the aims of this study.

\paragraph{Chapter \ref{ch:deep_learning_comparison} - Deep Learning Comparison} Compares our deep-learning approach with those benchmarked.

\paragraph{Chapter \ref{ch:validation_of_results} - Validation of Results} Highlights a number of validation techniques used to ensure results found in the comparison are correct.

\paragraph{Chapter \ref{ch:discussion} - Discussion and Limitations}Presents implications that were found from the results of our findings and possible limitations.

\paragraph{Chapter \ref{ch:conclusion} - Conclusions and Future Work} Draws a number of conclusions and alleviates gaps in the findings of this work by presenting future studies.