\chapter{Introduction}
\label{ch:introduction}

Ever since the camera and phone were unified into smartphones, we have seen an increasing interest for image understanding (specifically to identify the content of an image) but text recognition still faces challenges within images of unstructured scenes. While successes in character recognition have a long history with \gls{ocr} engines \citep{Smith:1987tg}, these are typically applied under strict conditions (e.g., flatbed scanners for documents without distracting backgrounds). Once applied within the context of a natural scene, real-world discrepancies pose serious shortcomings, such as illumination conditions, viewpoint and perspective differences, blur and glare variations, geometric and photometric distortion, and differences in font size and style \citep{Zhang:2008vfa, Jung:2004uw}. Overcoming these issues has motivated a variety of techniques to realise potential applications that make use of text recognition at scale.

With the ubiquity of smartphone cameras, practical applications of natural image processing have increased. In the last two decades, we have seen the development of point-and-shoot product recognition \citep{Tsai:2010cn,Girod:2011gw}, object detection in videos \citep{Sivic:2003tj}, building recognition \citep{Takacs:2008cg}, image feature extraction to improve visual-based search engines \citep{Lowe:2004kp,Bay:2008ud}, and translation services of American Sign Language gestures \citep{Jin:2016jd}. Nonetheless, embedded text within images contains indexable data on the image's semantics \citep{Smeulders:2000tx}; if text extraction is therefore not robust, information extraction suffers.

Text detection robustness is a factor which severely limits a text recognition pipeline. Research in overcoming such limitations have been competed numerous competitions \citep{Lucas:2003iw, Lucas:2005bq, Shahab:2011hq, Hua:2004vf}, where robustness is the key focus in the image processing pipelines proposed. This focus was reiterated by \citet{Chen:2011ul}, who state the primary prerequisite for text-based recognition (especially within natural scenes) is the text location must be robustly located.

As with any data processing pipeline, false negatives increase where early stages of the pipeline fail, and therefore detection of these potential candidates must be robust. We can reduce errors, and thus robustness, in a pipeline where: (1) there are unwarranted stages (\textit{excluding} unnecessary stages may also assist in reducing error cases) and (2) by piping through unmatched candidates to further pipelines, which can increase the detection.

Without the construct of robustness, we restrict these pipelines to very confined conditions, and its usefulness in products is not warranted. Therefore, the robustness of text extraction pipelines are imperative to gapping the semantic extraction of information from an image \citep{Smeulders:2000tx}, and solving this issue can assist in applications of image processing and data indexing of content within images \citep{Faloutsos:1994gr} of paramount proportions.

\input{mainmatter/introduction/background.tex}
\input{mainmatter/introduction/purpose.tex}
\input{mainmatter/introduction/research_goals.tex}
\input{mainmatter/introduction/thesis_organisation.tex}

\section*{Summary}

In this chapter we identified some shortcomings in text recognition, developed the context of the study---namely \gls{rbn} detection. We discussed the general stages that exist for text parsing within natural scenes, detection and recognition, and introduced typical techniques that are applied in this context. We outlined the research aims this study achieves, and how the thesis is organised. The following chapter will detail applications of image processing, using neural networks for image processing, and outline what techniques have been used in previous studies to achieve this.